EDIpack 2.0: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-20 01_intro.tex
Updates from Overleaf

%\paragraph{Interoperability}\\
With the growing importance of  quantum impurity models in the study of correlated materials,
standardizazion and interoperability between solution software suites has
become a critical necessity.
\NAME has been expressly designed following this guiding principle. 
While the library itself is implemented using modern Fortran constructs, it also provides an extensive set of C-bindings that enable integration with other programming languages,
be they compiled (C, C++), JIT-compiled (Julia) or interpreted (python). 
A significant contribution is realized via the Python API, EDIpy, which provides a high-level interface for defining and solving impurity problems. The
Python bindings also enable integration with established scientific
libraries, such as NumPy and SciPy, facilitating data analysis and
rapid prototyping.

A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, 
is the direct  interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems)  as
well as to the W2Dynamics software, which are two of the most 
important and used computational tools in the field. \NAME seamlessly slots in as an alternative
solver to the native Quantum Monte Carlo implementations, greatly extending the parameter (and 
especially temperature) range reachable by the simulation while minimizing code production from 
the end user.
At the same time, this integration provides \NAME users with access to the
extensive data handling and analysis tools in the TRIQS ecosystem. 
Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of achieving standardization for quantum impurity solvers.

>>>>

%\paragraph{Interoperability}\\
With the growing importance of  quantum impurity models in the study of correlated materials,
standardizazion and interoperability between solution software suites has
become a critical necessity.
\NAME has been expressly designed following this guiding principle. 
While the library itself is implemented using modern Fortran constructs, it also provides an extensive set of C-bindings that enable integration with other programming languages,
be they compiled (C, C++), JIT-compiled (Julia) or interpreted (Python). 
Especially notable in this sense is the Python API, EDIpy which, beyond providing a 
high-level interface for defining and solving impurity problems, also allows integration with established scientific libraries, such as NumPy and SciPy, facilitating data analysis and
rapid prototyping.

A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, 
is the direct  interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems) and
W2Dynamics software suites, which are two of the most important and used computational tools in
the field. \NAME seamlessly slots in as an alternative solver to the native Quantum Monte Carlo 
implementations, greatly extending the parameter (and especially temperature) range reachable by 
the simulation while minimizing the cfor the end user.
At the same time, this integration provides \NAME users with access to the
extensive data handling and analysis tools in the TRIQS ecosystem. 
Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of achieving standardization for quantum impurity solvers.
